% vim: ft=tex
\PassOptionsToPackage{prologue,dvipsnames}{xcolor}
\documentclass[acmsmall,natbib=false,review,anonymous]{acmart}
\input{../prelude.tex}

\newcommand{\ottDir}{../ott/_gen}
\newcommand{\genDir}{_gen}
\input{\ottDir/defs.tex}
\input{\ottDir/renew-ott.tex}

\begin{document}


\section{Syntax}

  \begin{supertabular}{rll p{0.8\textwidth}}
  \otte\\
  \ottA\\
  \end{supertabular}

\newpage

\section{Safety}

  To formulate the completeness properties (at some point in the future),
  we need to restrict the `implicit' binders $\lambda^{\forall}$ and $\forall$ 
  to bind variables that are at safe positions in the body.
  For this purpose, we define the well-formedness relation.

  Here $V$ is a set of variables,
  including normal variables ($\ottmv{x}$) 
  and safe variables ($\underline{x}$), whose positions are restricted.
  Overall, we wish to guarantee that 
  after normalization,
  substitution of safe variables
  does not produce new redexes. 

  The constructor forms are well-formed by congruence:
  if their components are well-formed.
  Notice that $\lambda^{\forall}$ and $\forall$ require 
  the bound variable to be safe in the body.

  The eliminator forms are well-formed 
  if their components are well-formed and 
  one of the following conditions hold:
  \begin{itemize}
    \item they do not contain variables that are required to be safe
    \item they are \emph{inert} (see below), which implies that 
      their outer structure withstands reduction and 
      substitution of safe variables.
    \item they are reducible but the reduction preserves safety:
      it does not eliminate metavariables, and if the substitution happens, 
      the variables we are substituting are at safe positions 
      and the terms we are substituting for are safe.
  \end{itemize}

    \ottdefnOkOKLabeled{}

  The types are not eliminated, so they behave as 
  constructor forms: they are well-formed by congruence.

    \ottdefnOkOKFLabeled{}

    The variables are always inert.
    The constructor forms are always inert. 

    Inert term preserve their outer structure under reduction 
    and substitution of safe variables. 
    Neutrally inert term, in addition, cannot be reduced when
    put in a redex position.

    \ottdefnOkNeuInertLabeled{}
    \ottdefnOkInertLabeled{}
\newpage

\section{Reduction}
  \label{sec:red}
  
  The reduction is defined in a standard way:
  we first reduce the components of terms (congruence rules),
  then we eliminate the redexes by the following rules.
  \begin{ottdefnblock}[]{\ottdefnHeaderRedRed}{}
    \ottusedrule{\ottdruleRedRedAppLamLabeled[]{}}
    \ottusedrule{\ottdruleRedRedAppPLamLabeled[]{}}
    \ottusedrule{\ottdruleRedRedSubstRedLabeled[]{}}
  \end{ottdefnblock}
  % (Here $cE$ is an evaluation context, i.e. a term with a hole 
  % in a term position; $cE \, \ottkw{is} \, \ottkw{safe}$ means that the hole is in a safe position)

  The invariants that we are preserving:
  \begin{itemize}
    \item reduction does not eliminate metavariables and the safe variables;
    \item reduction preserves safety of the metavariables and the safe variables.
  \end{itemize}


\subsection{Properties}

\begin{lemma}[Reduction preserves intertness]
\end{lemma}

\begin{lemma}[Safety is preserved when a safe term plugs into a safe position]
\end{lemma}

\begin{lemma}[Safety is preserved when a safe and neutrally inert term plugs into any position]
\end{lemma}

\begin{lemma}[Reduction preserves safety]
  If $V  \vdash  e_{{\mathrm{0}}} \, \ottkw{OK}$
  and $e_{{\mathrm{0}}}  \leadsto  e_{{\mathrm{1}}}$ then 
  $V  \vdash  e_{{\mathrm{1}}} \, \ottkw{OK}$.
  If $V  \vdash  A_{{\mathrm{0}}} \, \ottkw{OK}$
  and $A_{{\mathrm{0}}}  \leadsto  A_{{\mathrm{1}}}$ then
  $V  \vdash  A_{{\mathrm{1}}} \, \ottkw{OK}$.
\end{lemma}
\begin{proof}
  By induction on the reduction relation.
  \begin{itemize}
    \item If the last step of the reduction is a congruence rule
      on a constructor form
    (
      \ruleref{\ottdruleRedRedLamALabel}, 
      \ruleref{\ottdruleRedRedLameLabel},
      \ruleref{\ottdruleRedRedPLamALabel},
      \ruleref{\ottdruleRedRedPLameLabel},
      \ruleref{\ottdruleRedRedReflLabel}
    ) 
    then the safety of the metavariables
    is proved by the induction hypothesis and the corresponding 
    safety rule 
    (\ruleref{\ottdruleOkOKLamLabel}, 
     \ruleref{\ottdruleOkOKPLamLabel}, or
     \ruleref{\ottdruleOkOKReflLabel}).

    \item \ruleref{\ottdruleRedRedAppOneLabel}
    Then our term is the application $p_{{\mathrm{1}}} \, p_{{\mathrm{2}}}$,
    and its well-formedness is given by one of the two rules:
    \begin{itemize}
      \item \ruleref{\ottdruleOkOKAppNoSLabel}
        Then the well-formedness follows immediately 
        by the induction hypothesis applied to 
        $V  \vdash  p_{{\mathrm{1}}} \, \ottkw{OK}$.
      \item \ruleref{\ottdruleOkOKAppLabel}
        Then we will also need to prove 
          $p'_{{\mathrm{1}}} \, p_{{\mathrm{2}}} \, \ottkw{INERT}$,
    \end{itemize}

  \begin{itemize}

  \end{itemize}
\end{proof}

\newpage

\section{Normalization}

\begin{definition}
  $e$ is normalized if 
  there is no $e'$ such that $e  \leadsto  e'$.
\end{definition}

\begin{definition}
  $e'$ is a normal form of $e$ if
  $e  \leadsto^*  e'$ and $e'$ is normalized.
\end{definition}

\ottdefnRedNeutLabeled{}

\section{Well-formedness}

We define well-formedness of types and terms
in the standard congruent way.
The interesting part is the base case for the metavariables
(\ruleref{\ottdruleWfWFAVarLabel}),

  \begin{ottdefnblock}[]{\ottdefnHeaderWfWF}{}
    \ottusedrule{\ottdruleWfWFVarLabeled[]{}}
    \ottusedrule{\ottdruleWfWFPLamLabeled[]{}}
    \ottusedrule{\ottdruleWfWFAVarLabeled[]{}}
  \end{ottdefnblock}


\section{Metavariables and metasubstitution}

\begin{definition}
  Metasubstitution $M\sigma$
  is a mapping from metavariables to terms.
  The  specification 
  $\Gamma  \mathbin{;}  M\Gamma_{{\mathrm{2}}}  \vdash  M\sigma  \ottsym{:}  M\Gamma_{{\mathrm{1}}}$ states that
\end{definition}


\section{Conversion}

\begin{definition}
 $\Gamma  \mathbin{;}  M\Gamma  \vdash  e_{{\mathrm{0}}}  \equiv  e_{{\mathrm{1}}}$
 is defined as alpha-equivalence 
 transitively closed under reduction. 
\end{definition}



\section{Unification}


\begin{definition}
  Suppose that two terms $e_{{\mathrm{0}}}$ and 
  $e_{{\mathrm{1}}}$ are well-typed in the context $\Gamma$
  and metacontext $M\Gamma$, i.e., $\Gamma  \mathbin{;}  M\Gamma  \vdash  e_{{\mathrm{0}}}$
  and $\Gamma  \mathbin{;}  M\Gamma  \vdash  e_{{\mathrm{1}}}$.
  Then the metasubstitution $M\sigma_{{\mathrm{0}}}$ is a unifier
  of $e_{{\mathrm{0}}}$ and $e_{{\mathrm{1}}}$ if
  \begin{itemize}
    \item $\Gamma  \mathbin{;}  M\Gamma_{{\mathrm{0}}}  \vdash  M\sigma_{{\mathrm{0}}}  \ottsym{:}  M\Gamma$ and
    \item $\Gamma  \mathbin{;}  M\Gamma_{{\mathrm{0}}}  \vdash  \ottsym{[}  M\sigma_{{\mathrm{0}}}  \ottsym{]}  e_{{\mathrm{0}}}  \equiv  \ottsym{[}  M\sigma_{{\mathrm{0}}}  \ottsym{]}  e_{{\mathrm{1}}}$.
  \end{itemize}

  The unifier $M\sigma_{{\mathrm{0}}}$ is the most general if 
  for any other unifier $\Gamma  \mathbin{;}  M\Gamma_{{\mathrm{1}}}  \vdash  M\sigma_{{\mathrm{1}}}  \ottsym{:}  M\Gamma$ 
  of $e_{{\mathrm{0}}}$ and $e_{{\mathrm{1}}}$,
  there exists a metasubstitution $\Gamma  \mathbin{;}  M\Gamma_{{\mathrm{1}}}  \vdash  M\tau  \ottsym{:}  M\Gamma_{{\mathrm{0}}}$
  such that $\ottsym{Γ;}  M\Gamma_{{\mathrm{1}}}  \vdash  M\sigma_{{\mathrm{1}}}  \equiv  M\tau  \circ  M\sigma_{{\mathrm{0}}}$.
\end{definition}


\newpage

\appendix

\section{Appendix}

\ottdefnRedRedLabeled{}

\ottdefnWfWFLabeled{}

\end{document}